A practical look at genetic algorithms

### 2015-11-22 evolutionaryComputation/practicals/report.tex
finished the table
added a pargarph of speedup atempts

\section{Execution}
%TODO:
% 1. Experiments
% Make the actuall expiriment work\dots
%	Create tables % including:
%		* min pop size for 29 out of 30 runs successful.
%		* The average number of generations
%		* The average CPU time required for running the GA with minimal pop size
%		* average should be over 30 runs
%	Draw a graph from the experiments
%		* pop size on x, # succes on Y
% maybe some more testing of the crossovers?
% also try to implement a threading scheme??

>>>>

\subsection{Speed up attempts}
\subsubsection{Paralization}
Since were doing string comparisons I had the idea of ussing parlization to
speed up the algoritm by doing paralization. This can be done very easily
in scala with par collections (and the fact that imutibility is default).

However once I implemented this, I came to the conclusion it was not faster.
The overhead for delegating and creating threads was more than the parilization
gained.

The problem is that the evaluation function, even with gene length of 100, is
to cheap to make any reasonable paralization effecitve. However what was effictive
is the parilization of the expiriments. This reduced total runtime 
significantly. however this is not seen in the statistics.

\subsubsection{Evaluate each member on creation}
\section{Execution}
%TODO:
% 1. Experiments
% Use stoastic within the algoritm
%	Draw a graph from the experiments
%		* pop size on x, # succes on Y
% maybe some more testing of the crossovers?
% also try to implement a threading scheme??
